### 2019-11-29 Mathematical Statistics/ms_ch_04.rmd
mathematical statistics, ch4
mathematical statistics, ch4

@@

>>>>

f <- function(x) 2 / x^2

x <- seq( from = 1.01, to = 1.99, by = 0.001)

y <- f(x)

ggplot(data.table(x, y)) +
   geom_point(aes(x, y), color = "cornflowerblue", size = .6) +
   labs(title = "pdf f(x) = 2/x^2")

a <- cumsum(y) / sum(y)
p <- round( a[x == 1.5], 4 ) * 100

d <- data.table(x, y = a)
ggplot(d) +
   geom_point(aes(x, y), color = "cornflowerblue", size = .6) +
   geom_area(aes(x, y), data = d[x < 1.5], fill = "cornflowerblue", alpha = .3) +
   labs(title = paste("cdf f(x) = 2/x^2, A =", p ))

Numerical solution: `r p`%

@@

### 4.13

A random sample of size $n = 244$ is drawn from a distribution with pdf $f(x) = (3/16)(x - 4)^2, 2 \le x \le 6$.

Use the CLT approximation to estimate $P(X \ge 4.2)$.

### 4.14

According to the 2000 census, 28.6% of the US adult population recieved a high school diploma.

In a random sample of 800 US adults, what is the probability that between 220 and 230 (inclusive) people have a high school deploma?

Use the CLT approximation with continuity correction, and compare with the exact probility.

### 4.15

If $X_1, \ldots, X_n$ are i.i.d. from Unif[0, 1], how larage should n be so that $P(\bar{X} - \frac{1}{2} < 0.05) \ge 0.90$,

that is, is there at least a 90% chance that the sample mean is within 0.05 of $\frac{1}{2}$? Use the CLT approximation.
